### 2024-04-19 docs/SOSP 2024/results.tex
Some more latex hacking to save space

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.65\linewidth]{figures/geomean_speedup_T400_kernel_time.png}
  \caption{Speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
  benchmarks) across batch sizes on NVIDIA T400.}
  \label{Fig:TBvsRAPIDSTahoe_T400_Speedup}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.65\linewidth]{figures/speedup_vs_norm_time_line_graph_4060.png}
  \caption{Slowdown of heuristic schedule vs best schedule on NVIDIA RTX 4060 and 
  heuristic schedule exploration time normalized w.r.t full schedule exploration time}
  \label{Fig:HeuristicVsFullExplore_Speedup}
\end{figure}

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.65\linewidth]{figures/geomean_speedup_T400_4060_vs_T400_vs_MI2160.png}
  \caption{Geomean speedup of heuristic schedule on NVIDIA T400 and AMD MI2160 vs 
  the heuristic schedule on NVIDIA RTX 4060 across batch sizes}
  \label{Fig:AutotuningSpeedupvs4060Sched}
\end{figure}

>>>>

@@

\begin{figure*}[htb]
\begin{minipage}[t]{.3\linewidth}
  \centering
  \includegraphics[width=\linewidth]{figures/geomean_speedup_T400_kernel_time.png}
  \caption{Speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
  benchmarks) across batch sizes on NVIDIA T400.}
  \label{Fig:TBvsRAPIDSTahoe_T400_Speedup}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[t]{.3\linewidth}
  \centering
  \includegraphics[width=\linewidth]{figures/speedup_vs_norm_time_line_graph_4060.png}
  \caption{Slowdown of heuristic schedule vs best schedule on NVIDIA RTX 4060 and 
  heuristic schedule exploration time normalized w.r.t full schedule exploration time}
  \label{Fig:HeuristicVsFullExplore_Speedup}
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[t]{.3\linewidth}
  \centering
  \includegraphics[width=\linewidth]{figures/geomean_speedup_T400_4060_vs_T400_vs_MI2160.png}
  \caption{Geomean speedup of heuristic schedule on NVIDIA T400 and AMD MI2160 vs 
  the heuristic schedule on NVIDIA RTX 4060 across batch sizes}
  \label{Fig:AutotuningSpeedupvs4060Sched}
\end{minipage}
\end{figure*}
